Model LF

### 2022-11-02 Estimation.Rmd
commit

```{r}
reg_prod_start=dynlm(TSDELTALOG(prod) ~ 1 + L(TSDELTALOG(prod),1:4) +  L(TSDELTA(s_h),0:4)+  L(TSDELTALOG(mean_dp_regul),0:4)  + L(log(prod),1) + L(s_h,1)+ L(log(mean_dp_regul),1))

@@

 prod_vars_1 <- str_c("L(TSDELTALOG(prod), 1:4)", c(4))
 s_h_vars_1 <- str_c("L(TSDELTA(s_h), 0:4)", c(0))
 dp_person_vars_1 <- str_c("L(TSDELTALOG(mean_dp_regul), 0:4)", c(1,2,3,4))

@@

vars_out_1 <- c( prod_vars_1,s_h_vars_1,dp_person_vars_1 )
vars_out_1

@@

```{r}
reg_prod=dynlm(TSDELTALOG(prod) ~ 1 + L(TSDELTALOG(prod),2:3)  + L(log(prod),1) + L(s_h,1) + L(log(mean_dp_regul),1) + d_2007q4)

@@

```{r}
reg_prod_start=dynlm(TSDELTALOG(prod_ds) ~ 1 + L(TSDELTALOG(prod_ds),1:4) +  L(TSDELTALOG(mean_dp_regul),0:4) +  L(TSDELTALOG(y_ds),0:4) + L(log(prod_ds),1)+ L(log(y_ds),1) + L(log(mean_dp_regul),1))

@@

 prod_vars_1 <- str_c("L(TSDELTALOG(prod_ds), 1:4)", c(1,3))
 wage_ds_vars_1 <- str_c("L(TSDELTALOG(wage_ds), 0:4)", c(1:4))
 dp_person_vars_1 <- str_c("L(TSDELTALOG(mean_dp_regul), 0:4)", c(1:4))
  y_ds_vars_1 <- str_c("L(TSDELTALOG(y_ds), 0:4)", c(1:4))

@@

vars_out_1 <- c( prod_vars_1, wage_ds_vars_1,dp_person_vars_1 ,y_ds_vars_1)
vars_out_1

@@

```{r}
reg_prod=dynlm(TSDELTALOG(prod_ds) ~ 0 + L(TSDELTALOG(prod_ds),c(4)) +  L(TSDELTALOG(y_ds),0) + L(log(prod_ds),2)+ L(log(y_ds),2) + L(log(mean_dp_regul),2))

@@

>>>>

```{r}
reg_prod_start=dynlm(TSDELTALOG(prodk_ds) ~ 1 + L(TSDELTALOG(prodk_ds),1:4) +  L(TSDELTA(ur_ds),0:4)+  L(TSDELTALOG(wage_ds),0:4)  + L(log(prodk_ds),1) + L(ur_ds,1)+ L(log(wage_ds),1))

@@

 prod_vars_1 <- str_c("L(TSDELTALOG(prodk_ds), 1:4)", c(1,3))
 ur_ds_vars_1 <- str_c("L(TSDELTA(ur_ds), 0:4)", c(0,2))
 wage_ds_vars_1 <- str_c("L(TSDELTALOG(wage_ds), 0:4)", c(1,2,3,4))

@@

vars_out_1 <- c( prod_vars_1,ur_ds_vars_1,wage_ds_vars_1 )
vars_out_1

@@

```{r}
reg_prod=dynlm(TSDELTALOG(prodk_ds) ~ 0 + L(TSDELTALOG(prodk_ds),c(4)) +  L(TSDELTA(ur_ds),c(3))+  L(TSDELTALOG(wage_ds),0)  + L(log(prodk_ds),1) + L(ur_ds,1)+ L(log(wage_ds),1))

@@

```{r}
reg_prod_start=dynlm(TSDELTALOG(prod_ds) ~ 1 + L(TSDELTALOG(prod_ds),c(1:4)) + L(TSDELTA(s_h),c(0:4)) +  L(TSDELTALOG(mean_dp_regul),c(0:4))+ L(TSDELTALOG(wage_ds),c(0:4)) +  L(TSDELTALOG(y_ds),0:4) + L(log(prod_ds),2)+  L(log(wage_ds),2)+ L(log(y_ds),2) + L(s_h,2)+ L(log(mean_dp_regul),2))

@@

 prod_vars_1 <- str_c("L(TSDELTALOG(prod_ds), c(1:4))", c(1,3:4))
 dp_person_vars_1 <- str_c("L(TSDELTALOG(mean_dp_regul), c(0:4))", c(0:4))
  y_ds_vars_1 <- str_c("L(TSDELTALOG(y_ds), 0:4)", c(1,3))
  s_h_vars_1 <- str_c("L(TSDELTA(s_h), c(0:4))", c(0:4))
  wage_ds_vars_1 <- str_c("L(TSDELTALOG(wage_ds), c(0:4))", c(2:4))

@@

vars_out_1 <- c(wage_ds_vars_1, s_h_vars_1, prod_vars_1, dp_person_vars_1 , y_ds_vars_1)
vars_out_1

@@

```{r}
reg_prod=dynlm(TSDELTALOG(prod_ds) ~ 0 + L(TSDELTALOG(wage_ds),c(0)) +  L(TSDELTALOG(y_ds),c(0,4)) + L(log(prod_ds),2)+  L(log(wage_ds),2)+ L(log(y_ds),2) + L(log(mean_dp_regul),2))

@@

### Emp

```{r}
reg= dynlm(emp~yk + prodk)
summary(reg)
```

### 2022-11-02 max_dp endogen stød.Rmd
commit

IDENTITY> prodk_ds
EQ> prodk_ds=prod_ds * (yk_ds/y_ds)
IF> shock_prod_model > 0

@@

S_modelData$prod_shock = prod_ds

@@

```{r}
###Gengivelse af stød til model
part_bs1 = Shock_bs1$simulation$part
unemp_bs1 = Shock_bs1$simulation$unemp
komp_r_bs1 = Shock_bs1$simulation$komp_r
part_bs1 = Shock_bs1$simulation$part
yk_ds_bs1 = Shock_bs1$simulation$yk_ds
pc_ds_bs1 = Shock_bs1$simulation$pc_ds
wage_ds_t_bs1 = Shock_bs1$simulation$wage_ds_t
ur_ds_bs1 = Shock_bs1$simulation$ur_ds
emp_bs1 = Shock_bs1$simulation$emp
yd_hk_ds_bs1 = Shock_bs1$simulation$yd_hk_ds
pconk_ds_bs1= Shock_bs1$simulation$pconk_ds
tilpas_pr_bs1 = Shock_bs1$simulation$tilpas_pr
u_ds_bs1 = Shock_bs1$simulation$u_ds
part_bs1 = Shock_bs1$simulation$part
nben_h_bs1 = Shock_bs1$simulation$nben_h
wage_ds_bs1 = Shock_bs1$simulation$wage_ds
dp_person_bs1 = Shock_bs1$simulation$dp_person
kont_h_ratio_bs1 = Shock_bs1$simulation$kont_h_ratio
unemp_bs1 = Shock_bs1$simulation$unemp
nl_g_bs1 = Shock_bs1$simulation$nl_g
inflation_bs1 = Shock_bs1$simulation$inflation
lf_bs1 = Shock_bs1$simulation$lf
yd_hk_ds_bs1 = Shock_bs1$simulation$yd_hk_ds
wage_gap1_bs1 = Shock_bs1$simulation$wage_gap1
wage_gap_bs1 = Shock_bs1$simulation$wage_gap
prod_bs1 = Shock_bs1$simulation$prod
prod_bs1 = Shock_bs1$simulation$prod

@@

nl_g_bs7 = Shock_bs7$simulation$nl_g
unemp_bs7 = Shock_bs7$simulation$unemp
yd_hk_ds_bs7 = Shock_bs7$simulation$yd_hk_ds
wage_gap1_bs7 = Shock_bs7$simulation$wage_gap1
wage_gap_bs7 = Shock_bs7$simulation$wage_gap
prod_bs7 = Shock_bs7$simulation$prod
```

@@

```{r}
###Gengivelse af stød til model
max_dp_bs7b = Shock_bs7b$simulation$max_dp
wage_bs7b = Shock_bs7b$simulation$wage
komp_r_bs7b = Shock_bs7b$simulation$komp_r
part_bs7b = Shock_bs7b$simulation$part
yk_ds_bs7b = Shock_bs7b$simulation$yk_ds
pc_ds_bs7b = Shock_bs7b$simulation$pc_ds
wage_ds_t_bs7b = Shock_bs7b$simulation$wage_ds_t
ur_ds_bs7b = Shock_bs7b$simulation$ur_ds
emp_bs7b = Shock_bs7b$simulation$emp
yd_hk_ds_bs7b = Shock_bs7b$simulation$yd_hk_ds
prodk_bs7b = Shock_bs7b$simulation$prodk
tilpas_pr_bs7b = Shock_bs7b$simulation$tilpas_pr
u_ds_bs7b = Shock_bs7b$simulation$u_ds
part_bs7b = Shock_bs7b$simulation$part
nben_h_bs7b = Shock_bs7b$simulation$nben_h
wage_ds_bs7b = Shock_bs7b$simulation$wage_ds
dp_person_bs7b = Shock_bs7b$simulation$dp_person
kont_h_ratio_bs7b = Shock_bs7b$simulation$kont_h_ratio
lf_bs7b = Shock_bs7b$simulation$lf
nl_g_bs7b = Shock_bs7b$simulation$nl_g
unemp_bs7b = Shock_bs7b$simulation$unemp
yd_hk_ds_bs7b = Shock_bs7b$simulation$yd_hk_ds
wage_gap1_bs7b = Shock_bs7b$simulation$wage_gap1
wage_gap_bs7b = Shock_bs7b$simulation$wage_gap
prod_bs7b = Shock_bs7b$simulation$prod
ur_test_bs7b = Shock_bs7b$simulation$ur_test
ur_bs7b = Shock_bs7b$simulation$ur
```

@@

nl_g_000 = Shock_0$simulation$nl_g

yd_hk_ds_000 = Shock_0$simulation$yd_hk_ds
wage_gap1_000 = Shock_0$simulation$wage_gap1
wage_gap_000 = Shock_0$simulation$wage_gap
prod_000 = Shock_0$simulation$prod
```

```{r}
plot(part_000, col= "red"); lines(part_bs1, col = "blue");
legend("top",legend=c("Baseline", "Data"),lty=c(1,1),lwd=c(2),bty="n", col = c("red", "blue")); 
grid()
```
```{r}

@@

yk_ds_07b = Shock_7b$simulation$yk_ds
emp_07b = Shock_7b$simulation$emp
wage_ds_07b= Shock_7b$simulation$wage_ds
ur_ds_07b = Shock_7b$simulation$ur_ds
pc_ds_07b = Shock_7b$simulation$pc_ds
yd_hk_ds_07b = Shock_7b$simulation$yd_hk_ds
pconk_ds_07b = Shock_7b$simulation$pconk_ds
komp_r_07b = Shock_7b$simulation$komp_r
max_dp_07b = Shock_7b$simulation$max_dp
nben_h_07b = Shock_7b$simulation$nben_h
yd_hk_ds_07b = Shock_7b$simulation$yd_hk_ds
ik_07b = Shock_7b$simulation$ik
wage_ds_t_07b = Shock_7b$simulation$wage_ds_t
nben_h_un_07b = Shock_7b$simulation$nben_h_un
nl_g_07b = Shock_7b$simulation$nl_g
nsben_h_07b = Shock_7b$simulation$nsben_h
dp_person_07b = Shock_7b$simulation$dp_person
u_ds_07b = Shock_7b$simulation$u_ds
shock_kuld_07b = Shock_7b$simulation$shock_kuld
unemp_07b = Shock_7b$simulation$unemp
lf_07b = Shock_7b$simulation$lf
part_07b = Shock_7b$simulation$part

prod_07b = Shock_7b$simulation$prod
```

@@

```{r}
plot(((prod_07b - prod_bs7b)), col= "blue", xlab= "Year", ylab= "Change in labor force (people)", main= "Change in Labor force");
grid()
```

>>>>

IDENTITY> prodk_ds
EQ> prodk_ds=prod_ds * (yk_ds/y_ds)
IF> shock_prod_model > 0
IDENTITY> prodk_ds
EQ> prodk_ds=prod_ds * (yk_ds/y_ds)
IF> shock_lf_model > 0

@@

#S_modelData$prod_shock = prod_ds

@@

```{r}
###Gengivelse af stød til model
part_bs1 = Shock_bs1$simulation$part
unemp_bs1 = Shock_bs1$simulation$unemp
komp_r_bs1 = Shock_bs1$simulation$komp_r
part_bs1 = Shock_bs1$simulation$part
yk_ds_bs1 = Shock_bs1$simulation$yk_ds
pc_ds_bs1 = Shock_bs1$simulation$pc_ds
wage_ds_t_bs1 = Shock_bs1$simulation$wage_ds_t
ur_ds_bs1 = Shock_bs1$simulation$ur_ds
emp_bs1 = Shock_bs1$simulation$emp
yd_hk_ds_bs1 = Shock_bs1$simulation$yd_hk_ds
pconk_ds_bs1= Shock_bs1$simulation$pconk_ds
tilpas_pr_bs1 = Shock_bs1$simulation$tilpas_pr
u_ds_bs1 = Shock_bs1$simulation$u_ds
part_bs1 = Shock_bs1$simulation$part
nben_h_bs1 = Shock_bs1$simulation$nben_h
wage_ds_bs1 = Shock_bs1$simulation$wage_ds
dp_person_bs1 = Shock_bs1$simulation$dp_person
kont_h_ratio_bs1 = Shock_bs1$simulation$kont_h_ratio
unemp_bs1 = Shock_bs1$simulation$unemp
nl_g_bs1 = Shock_bs1$simulation$nl_g
inflation_bs1 = Shock_bs1$simulation$inflation
lf_bs1 = Shock_bs1$simulation$lf
yd_hk_ds_bs1 = Shock_bs1$simulation$yd_hk_ds
wage_gap1_bs1 = Shock_bs1$simulation$wage_gap1
wage_gap_bs1 = Shock_bs1$simulation$wage_gap
prod_bs1 = Shock_bs1$simulation$prod
prodk_ds_bs1 = Shock_bs1$simulation$prodk_ds

@@

nl_g_bs7 = Shock_bs7$simulation$nl_g
unemp_bs7 = Shock_bs7$simulation$unemp
yd_hk_ds_bs7 = Shock_bs7$simulation$yd_hk_ds
wage_gap1_bs7 = Shock_bs7$simulation$wage_gap1
wage_gap_bs7 = Shock_bs7$simulation$wage_gap
prodk_bs7 = Shock_bs7$simulation$prodk
```

@@

```{r}
###Gengivelse af stød til model
max_dp_bs7b = Shock_bs7b$simulation$max_dp
wage_bs7b = Shock_bs7b$simulation$wage
komp_r_bs7b = Shock_bs7b$simulation$komp_r
part_bs7b = Shock_bs7b$simulation$part
yk_ds_bs7b = Shock_bs7b$simulation$yk_ds
pc_ds_bs7b = Shock_bs7b$simulation$pc_ds
wage_ds_t_bs7b = Shock_bs7b$simulation$wage_ds_t
ur_ds_bs7b = Shock_bs7b$simulation$ur_ds
emp_bs7b = Shock_bs7b$simulation$emp
yd_hk_ds_bs7b = Shock_bs7b$simulation$yd_hk_ds
prodk_bs7b = Shock_bs7b$simulation$prodk
tilpas_pr_bs7b = Shock_bs7b$simulation$tilpas_pr
u_ds_bs7b = Shock_bs7b$simulation$u_ds
part_bs7b = Shock_bs7b$simulation$part
nben_h_bs7b = Shock_bs7b$simulation$nben_h
wage_ds_bs7b = Shock_bs7b$simulation$wage_ds
dp_person_bs7b = Shock_bs7b$simulation$dp_person
kont_h_ratio_bs7b = Shock_bs7b$simulation$kont_h_ratio
lf_bs7b = Shock_bs7b$simulation$lf
nl_g_bs7b = Shock_bs7b$simulation$nl_g
unemp_bs7b = Shock_bs7b$simulation$unemp
yd_hk_ds_bs7b = Shock_bs7b$simulation$yd_hk_ds
wage_gap1_bs7b = Shock_bs7b$simulation$wage_gap1
wage_gap_bs7b = Shock_bs7b$simulation$wage_gap
prod_bs7b = Shock_bs7b$simulation$prod
ur_test_bs7b = Shock_bs7b$simulation$ur_test
ur_bs7b = Shock_bs7b$simulation$ur

y_bs7b = Shock_bs7b$simulation$y
yk_bs7b = Shock_bs7b$simulation$yk

y_yk_bs7= yk_bs7b/y_bs7b
```

@@

nl_g_000 = Shock_0$simulation$nl_g
prodk_ds_000 = Shock_0$simulation$prodk_ds
yd_hk_ds_000 = Shock_0$simulation$yd_hk_ds
wage_gap1_000 = Shock_0$simulation$wage_gap1
wage_gap_000 = Shock_0$simulation$wage_gap
prod_000 = Shock_0$simulation$prod
```

```{r}
plot(prodk_ds_000, col= "red"); lines(prodk_ds_bs1, col = "blue");
legend("top",legend=c("Baseline", "Data"),lty=c(1,1),lwd=c(2),bty="n", col = c("red", "blue")); 
grid()
```
```{r}

@@

yk_ds_07b = Shock_7b$simulation$yk_ds
emp_07b = Shock_7b$simulation$emp
wage_ds_07b= Shock_7b$simulation$wage_ds
ur_ds_07b = Shock_7b$simulation$ur_ds
pc_ds_07b = Shock_7b$simulation$pc_ds
yd_hk_ds_07b = Shock_7b$simulation$yd_hk_ds
pconk_ds_07b = Shock_7b$simulation$pconk_ds
komp_r_07b = Shock_7b$simulation$komp_r
max_dp_07b = Shock_7b$simulation$max_dp
nben_h_07b = Shock_7b$simulation$nben_h
yd_hk_ds_07b = Shock_7b$simulation$yd_hk_ds
ik_07b = Shock_7b$simulation$ik
wage_ds_t_07b = Shock_7b$simulation$wage_ds_t
nben_h_un_07b = Shock_7b$simulation$nben_h_un
nl_g_07b = Shock_7b$simulation$nl_g
nsben_h_07b = Shock_7b$simulation$nsben_h
dp_person_07b = Shock_7b$simulation$dp_person
u_ds_07b = Shock_7b$simulation$u_ds
shock_kuld_07b = Shock_7b$simulation$shock_kuld
unemp_07b = Shock_7b$simulation$unemp
lf_07b = Shock_7b$simulation$lf
part_07b = Shock_7b$simulation$part
yk_07b = Shock_7b$simulation$yk
y_07b = Shock_7b$simulation$y
prodk_07b = Shock_7b$simulation$prodk

y_yk_07b=yk_07b/y_07b
```

@@

```{r}
plot(((y_yk_07b - prodk_bs7b)), col= "blue", xlab= "Year", ylab= "Change in labor force (people)", main= "Change in Labor force");
grid()
```

```{r}
plot( y_yk_07b, col= "blue", xlab= "Year", ylab= "Change in Unemployment (people)", main= "Change in Unemployment");
lines(y_yk_bs7, col= "black");
legend("left", legend=c("Productivity channel", "All channels"),
       lty=c(1),lwd=c(2),bty="n", col = c("blue","black","red", "green"));
grid()
```
